mouse_microbiome

### 2018-07-06 Manuscript_Mouse_Microbiome.Rmd
fixes

@@

# load packages and custom functions
wd <- 'C:\\Users\\John\\Documents\\msu\\mouse_microbiome\\'
source(paste0(wd, 'custom_functions.R'))
loadpax(pkg = c('tidyverse','knitr','data.table','vegan', 'ape'))

@@

p <- x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(!is.na(Pair) & abun > 0 & status_recovery != 'absent') %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Pair = paste('Pair', Pair),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), y = abun, fill = OTU_status)) +
    geom_bar(stat='identity', alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_grid(Abx~Pair) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'Rarefied abundance') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTUAbunByAbxStatus', dir = image_dir, width = 6.5, height = 5)

@@

x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(Abx == 'Y' & abun > 0 & status_recovery != 'absent' & Mouse != 1) %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Mouse = paste(ifelse(Cohoused == 'Y', 'Cohoused', 'Not cohoused'), "- Mouse", Mouse),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), y = abun, fill = OTU_status)) +
    geom_bar(stat='identity', alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_wrap(~Mouse, ncol = 5) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'Rarefied abundance') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTUAbunByCageStatus', dir = image_dir, width = 6.5, height = 5)

@@

x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(!is.na(Pair) & abun > 0 & status_recovery != 'absent') %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Pair = paste('Pair', Pair),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), fill = OTU_status)) +
    geom_bar(alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_grid(Abx~Pair) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'OTU richness') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTURichByAbxStatus', dir = image_dir, width = 6.5, height = 5)

@@

x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(Abx == 'Y' & abun > 0 & status_recovery != 'absent' & Mouse != 1) %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Mouse = paste(ifelse(Cohoused == 'Y', 'Cohoused', 'Not cohoused'), "- Mouse", Mouse),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), fill = OTU_status)) +
    geom_bar(alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_wrap(~Mouse, ncol = 5) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'OTU richness') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTURichByCageStatus', dir = image_dir, width = 6.5, height = 5)

>>>>

knitr::opts_chunk$set(cache = TRUE)

@@

# load packages and custom functions
wd <- 'C:\\Users\\John\\Documents\\msu\\Mouse_Microbiome\\'
setwd(wd)

source(paste0(wd, 'custom_functions.R'))
loadpax(pkg = c('tidyverse','knitr','data.table','vegan', 'ape'))

@@

p <- x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(!is.na(Pair) & abun > 0 & status_recovery != 'absent') %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144)')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Pair = paste('Pair', Pair),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), y = abun, fill = OTU_status)) +
    geom_bar(stat='identity', alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_grid(Pair~Abx) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'Rarefied abundance') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTUAbunByAbxStatus', dir = image_dir, width = 7, height = 7)

@@

p <- x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(Abx == 'Y' & abun > 0 & status_recovery != 'absent' & Mouse != 1) %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144)')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Mouse = paste(ifelse(Cohoused == 'Y', 'Cohoused', 'Not cohoused'), "- Mouse", Mouse),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), y = abun, fill = OTU_status)) +
    geom_bar(stat='identity', alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_wrap(~Mouse, ncol = 2) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'Rarefied abundance') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTUAbunByCageStatus', dir = image_dir, width = 7, height = 7)

@@

p <- x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(!is.na(Pair) & abun > 0 & status_recovery != 'absent') %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144)')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Pair = paste('Pair', Pair),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), fill = OTU_status)) +
    geom_bar(alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_grid(Pair~Abx) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'OTU richness') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTURichByAbxStatus', dir = image_dir, width = 7, height = 7)

@@

p <- x %>%
  ungroup() %>%
  left_join(j[, c('Mouse','otu','status_recovery','immigrant_type')], by = c('Mouse','otu')) %>%
  filter(Abx == 'Y' & abun > 0 & status_recovery != 'absent' & Mouse != 1) %>%
  arrange(status_recovery) %>%
  mutate(status_recovery = ifelse(status_recovery == 'immigrant', immigrant_type, status_recovery)) %>%
  mutate(OTU_status = c('Extinct by end of Abx treatment (hour 120 at the latest); does not return during recovery period', 
                        'New colonist, arrived during recovery period (after hour 120)',
                        'Present throughout experiment',
                        'Extinct during end of Abx treatment (between Hours 63-120); returns during recovery period (after Hour 144)')[match(as.numeric(factor(status_recovery, levels = sort(unique(status_recovery)))), c(1:4))],
         Mouse = paste(ifelse(Cohoused == 'Y', 'Cohoused', 'Not cohoused'), "- Mouse", Mouse),
         Abx = ifelse(Abx == 'Y', 'Abx', 'No abx')) %>%
  ggplot(aes(x = as.factor(Hour), fill = OTU_status)) +
    geom_bar(alpha = 0.8) +
    geom_rect(xmin = 0, xmax = 14, ymin = -100, ymax = 0, fill = 'red', alpha = 0.2) +
    facet_wrap(~Mouse, ncol = 2) +
    scale_fill_manual(name = '', values = c('#a6611a','#dfc27d','#80cdc1','#018571')) +
    #scale_fill_discrete(name = '') +
    labs(x = 'Hour: {0,4,8,12,16,20,23,25,39,49,63,73,97,120,144,168,192,216,240,312}', y = 'OTU richness') +
    guides(fill=guide_legend(nrow=4,byrow=TRUE, position = 'bottom')) +
    theme_bw() +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_blank(),
      axis.text.x=element_blank(),
      legend.position = 'bottom')

plot_it(p, name = 'figOTURichByCageStatus', dir = image_dir, width = 7, height = 7)
